\sysfull

### 2018-08-03 paper/asplos19/intro.tex
first iteration on challenges and contributions

%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
\textbf{Challenges.} While a compiler can use static data privatization and commit instrumentation
(i.e., redo-logging) to eliminate statically identifiable, inter-task data
dependences~\cite{alpaca}, a \emph{dynamic} dependence between two coalesced
tasks requires dynamic privatization and commit actions.
%
To ensure consistency and respect inter-task dependences, \sys uses a novel
approach \emph{power failure-immune memory virtualization} that buffers non-volatile variable
updates in volatile memory during a coalesced task execution, before committing
them to non-volatile memory at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.
A static task decomposition model assumes that each
single task can execute to completion. If the hardware energy buffer provides
inadequate energy to execute each single task to completion, a program will not
terminate~\cite{cleancut_2018}. To avoid non-termination under adversarial
energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
Partial execution avoids non-termination by committing the intermediate state of a long-running
task that has repeatedly failed and restarted. Partial execution violates
task atomicity, but preserves forward progress; if a programmer knows that
task atomicity is crucial to correctness, they can disable partial execution around a piece of code.
%
% !!!! % It should be emphasized that unlike a voltage-threshold-based protection approaches that may suffer from a non-termination problem if the checkpoint has to be placed within the interrupt-disabled region, a timer-based approach adapts its partial commit location on repeated failures.
%
%Task coalescing removes the burden from the programmer, because it accepts any
%task decomposition and improves it dynamically. To further reduce the
%programmer effort, we propose a compiler pass for \emph{automatic
%decomposition} of programs into (small) \emph{atomic} tasks. The compiler
%identifies non-volatile variables shared across tasks as tasks are created, and
%instruments reads and writes of those variables, using memory virtualization,
%to keep the data consistent in the presence of power loss.
%
%\textcolor{red}{Despite being limited to a subset of the C language, the
%automatic task decomposition allowed us to port several	applications to an
%intermittent platform with a moderate effort.}
%

\textbf{Contributions.} To summarize, \sys's main contributions are:
%
\begin{itemize}
\item The first {\em adaptive} task-based intermittent execution model that
dynamically \emph{coalesces} tasks to reduce commit overhead and
\emph{downscales} tasks to ensure forward progress.
\item The first memory virtualization mechanism that preserves the atomicity of coalesced tasks under power failures.
%\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
\item A fully-realized prototype of \sys that runs on real energy-harvesting devices, to be released as open source after publication via~\cite{coala_website}.
\item An evaluation directly comparing \sys to a state of the art task-based
intermittent programming and execution model from prior work, showing that on a
suite of benchmarks from the literature and several new workloads, \sys often
has higher performance and is more flexible to diverse energy conditions.
\end{itemize}
%
Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while
Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism (coalescing and downscaling). Memory virtualization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
context of related work and Section~\ref{sec:conclusions} concludes and discusses
future work.

>>>>

%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
\textbf{Challenges and Contributions} 
\begin{itemize}
\item\textit{challenge} 1) Given unpredictable energy shots arrival, how to specify the size of a dynamic task on the fly? \textit{contribution---1} \sys addresses this challenge by using its \textit{recent execution history} as a metric to estimate the environment energy conditions. Furthermore, It mitigates the risk of dynamic task re-execution by taking advantage of the certainty that the energy buffer offers and approaches the expected power interrupt carefully. 
%
\item\textit{challenge} 2) Given dynamic variables dependencies, how to ensure efficient data protection against power interrupts? \textit{contribution---2} \sys ensures the consistency of the data by using a novel
approach called \emph{dynamic group privatization}. Varying variables dependencies forces a static approach (i.e.~\cite{alpaca}) to operate by considering a worst case scenario (i.e. protecting all global variables) in each dynamic task transition. \sys, therefore, utilizes a real-time data tracking to enable partial data protection on a task transition. Individual variables tacking, however, slows down a system dramatically. Therefore, \sys  relies on a coarse locality principle and protects the global variables in a batch. Moreover, it optimizes the data transfer by using Direct Memory Access (DMA).

\item\textit{challenge} 3) A static task decomposition model assumes that each
single task can execute to completion. If the hardware energy buffer provides
inadequate energy to execute each single task to completion, a program will not
terminate~\cite{cleancut_2018}. under such conditions how to enable the dynamic execution model to progress on a sub-task level? \textit{contribution---3} To avoid non-termination under adversarial
energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
Partial execution avoids non-termination by committing the intermediate state of a long-running
task that has repeatedly failed and restarted. Partial execution violates
task atomicity, but preserves forward progress; if a programmer knows that
task atomicity is crucial to correctness, they can disable partial execution around a piece of code.

% \textbf{dynamic privatization}: while a compiler can use static data privatization and commit instrumentation
% (i.e., redo-logging) to eliminate statically identifiable, inter-task data
% dependences~\cite{alpaca}, a \emph{dynamic} dependence between two coalesced
% tasks requires dynamic privatization and commit actions.
% %

%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.
% \textbf{task non-termination}:

%
% !!!! % It should be emphasized that unlike a voltage-threshold-based protection approaches that may suffer from a non-termination problem if the checkpoint has to be placed within the interrupt-disabled region, a timer-based approach adapts its partial commit location on repeated failures.
%
%Task coalescing removes the burden from the programmer, because it accepts any
%task decomposition and improves it dynamically. To further reduce the
%programmer effort, we propose a compiler pass for \emph{automatic
%decomposition} of programs into (small) \emph{atomic} tasks. The compiler
%identifies non-volatile variables shared across tasks as tasks are created, and
%instruments reads and writes of those variables, using memory virtualization,
%to keep the data consistent in the presence of power loss.
%
%\textcolor{red}{Despite being limited to a subset of the C language, the
%automatic task decomposition allowed us to port several	applications to an
%intermittent platform with a moderate effort.}
%
\end{itemize}

% \textbf{Contributions.} To summarize, \sys's main contributions are:
% %
% \begin{itemize}
% \item The first {\em adaptive} task-based intermittent execution model that
% dynamically \emph{coalesces} tasks to reduce commit overhead and
% \emph{downscales} tasks to ensure forward progress.
% \item The first memory virtualization mechanism that preserves the atomicity of coalesced tasks under power failures.
% %\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
% \item A fully-realized prototype of \sys that runs on real energy-harvesting devices, to be released as open source after publication via~\cite{coala_website}.
% \item An evaluation directly comparing \sys to a state of the art task-based
% intermittent programming and execution model from prior work, showing that on a
% suite of benchmarks from the literature and several new workloads, \sys often
% has higher performance and is more flexible to diverse energy conditions.
% \end{itemize}
%
Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while
Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism (coalescing and downscaling). Memory virtualization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
context of related work and Section~\ref{sec:conclusions} concludes and discusses
future work.
